Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-17 ebayes_rnaseq_heterosis.tex
first stab at abstract

\pagerange{\pageref{firstpage}--\pageref{lastpage}} 
\volume{VV}
\pubyear{YYYY}
\artmonth{Month}
\doi{x}

@@

%  put the summary for your paper here

\begin{abstract}
This is the summary for this paper.
\end{abstract}

>>>>

\pagerange{\pageref{firstpage}--\pageref{lastpage}} 
\volume{VV}
\pubyear{YYYY}
\artmonth{MM}
\doi{x}

@@

\begin{abstract}
Heterosis, or hybrid vigor, refers to the enhances phenotype of hybrid progeny relative to their inbred parents. The heterosis phenomenon is extensively utilized in agriculture though the molecular basis is still unknown. In an effort to understand phenotypic heterosis at the molecular level, researchers have begun to compare expression levels of thousands of genes between parental inbred lines and their hybrid offspring to search for evidence of gene expression heterosis in RNA sequencing (RNAseq) experiments. Standard statistical approaches for RNAseq experiments have difficulty with the composite null hypothesis for gene heterosis testing. To address these shortcomings, we develop a hierarchical model based on negative-binomial data model and a computationally tractible empirical Bayes approach to evaluating gene heterosis hypotheses. We demonstrate improvements over alternative methods via a simulation study based on a maize experiment, and then analyze that maize experiment. This article has supplementary material online. 
\end{abstract}
